Manuscript draft

### 2019-06-20 manuscript/manuscript draft.Rmd
updated manuscript draft

  ```{r echo=FALSE, out.width='100%', fig.cap = "Map showing all data used in the analysis, coded by variable", fig.pos='H'}
  knitr::include_graphics("distribution_all_variables.png")
  ```
*Data selection.* Over 50 variables of forest carbon stocks and annual fluxes are represented in the ForC database; this analysis focussed on measures of primary productivity. Table 1 contains details of the variables selected for analysis.

| Variable | Definition | Components included | Methodologies used|
|--------------|-------------------|-------------|------------------------|
| GPP | Annual gross primary production; annual uptake of carbon dioxide by an ecosystem | NA | Flux partitioning of eddy covariance |
| NPP | Annual net primary production; the component of GPP that is stored in plant tissue; GPP minus ecosystem respiration | Foliage, branch, stem, coarse root, fine root, and optionally understory | Direct measurement of annual increments of components | 
| ANPP | Aboveground net primary production | Foliage, stem, and optionally branch | Direct measurement of annual increments of components | 
| ANPP_foliage | Net primary production of foliage | Foliage | Direct measurement of litterfall, correcting for changes in leaf biomass when measured |
| ANPP_woody | Net primary production of woody components | Stems and branches | Direct measurement of stem growth and branch fall |
| ANPP_woody_stem | Net primary production of woody stems | Woody stems | Direct measurement of stem growth increment |
| BNPP_root | Belowground net primary production | Coarse and fine roots | Direct measurement of one or more of: fine root turnover, soil cores, root ingrowth cores, minirhizotrons; indirect estimates of coarse roots using allometries based on aboveground stem increment measures |
| BNPP_root_fine | Net primary production of fine roots | Fine roots | Direct measurement of one or more of: minirhizotrons, fine root turnover, soil cores, root ingrowth cores |

@@

@@

  ```{r echo=FALSE, out.width='100%', fig.cap = "Graph to show primary productivity $(MgCha^-1^yr^-1^)$ regressed against latitude. Lines of best fit are plotted according to the best model selected during analysis. All regressions are significant $(p<0.05)$.", fig.pos='H'}
  knitr::include_graphics("effect_of_latitude.png")
  ```

@@

@@

  ```{r echo=FALSE, out.width='100%', fig.cap = "Plots of primary productivity $(MgCha^-1^yr^-1^)$ regressed against the climate variables identified as the best predictors. Lines of best fit are plotted according to the best model selected during analysis. All regressions are significant $(p<0.05)$.", fig.pos='H'}
  knitr::include_graphics("combined_plots.png")
  ```

**Temperature seasonality**  
**Mean annual temperature**  
**Annual temperature range**  
**Vapour pressure**

>>>>

  ```{r echo=FALSE, out.width='100%', fig.cap = "Map showing all data used in the analysis, coded by variable", fig.pos='H'}
  knitr::include_graphics("distribution_all_variables.png")
  ```
*Data selection.* Over 50 variables of forest carbon stocks and annual fluxes are represented in the ForC database; this analysis focussed on measures of primary productivity. Table 1 contains details of the variables selected for analysis. For the purposes of analysis, all estimates of NPP_1 and NPP_2 were combined as NPP, and all estimates of ANPP_1 and ANPP_2 were combined as ANPP.

| Variable | Definition | Components included | Methodologies used|
|--------------|-------------------|-------------|------------------------|
| GPP | Annual gross primary production; annual uptake of carbon dioxide by an ecosystem | NA | Flux partitioning of eddy covariance |
| NPP_1 | Annual net primary production; the component of GPP that is stored in plant tissue; GPP minus ecosystem respiration | Foliage, branch, stem, coarse root and fine root | Direct measurement of annual increments of components | 
| NPP_2 | Annual net primary production; the component of GPP that is stored in plant tissue; GPP minus ecosystem respiration | Foliage, branch, stem, coarse root, fine root, and understory | Direct measurement of annual increments of components |
| ANPP_1 | Aboveground net primary production | Foliage and stem | Direct measurement of annual increments of components | 
| ANPP_2 | Aboveground net primary production | Foliage, stem, and branch | Direct measurement of annual increments of components |
| ANPP_foliage | Net primary production of foliage | Foliage | Direct measurement of litterfall, correcting for changes in leaf biomass when measured |
| ANPP_woody | Net primary production of woody components | Stems and branches | Direct measurement of stem growth and branch fall |
| ANPP_woody_stem | Net primary production of woody stems | Woody stems | Direct measurement of stem growth increment |
| BNPP_root | Belowground net primary production | Coarse and fine roots | Direct measurement of one or more of: fine root turnover, soil cores, root ingrowth cores, minirhizotrons; indirect estimates of coarse roots using allometries based on aboveground stem increment measures |
| BNPP_root_fine | Net primary production of fine roots | Fine roots | Direct measurement of one or more of: minirhizotrons, fine root turnover, soil cores, root ingrowth cores |

@@

*Validating models of component fluxes.* Comparison of component fluxes is based on the assumption that components sum accurately to estimates of larger fluxes. To test this, components of larger fluxes were regressed against latitude, and the models used to generate a series of point estimates along lines of best fit for each component. The point estimates for smaller component fluxes were summed to generate new "stacked" estimates of larger fluxes, which were then compared against actual measurements of the larger flux. Confidence intervals for the larger flux were calculated using the 'bootMer' function from the lme4 package. Stacked plots were generated for:  
1. ANPP_2 + BNPP_root = NPP_1  
2. ANPP_foliage + ANPP_woody_stem = ANPP_1  
3. NPP_1 + R_auto = GPP

@@

  ```{r echo=FALSE, out.width='100%', fig.cap = "Graph to show primary productivity $(MgC~ha^-1~yr^-1)$ regressed against latitude. Lines of best fit are plotted according to the best model selected during analysis. All regressions are significant $(p<0.05)$.", fig.pos='H'}
  knitr::include_graphics("effect_of_latitude.png")
  ```

@@

Analysis of component fluxes indicates that measures of smaller component fluxes do approximately sum to measures of larger fluxes (fig. 3). Modelled estimates of NPP, generated from the sum of ANPP and BNPP~root~, and ANPP, generated from the sum of ANPP~foliage~ and ANPP~woodystem~, fall completely within the confidence intervals of the regressions of field estimates of NPP and ANPP.

  ```{r echo=FALSE, out.width='100%', fig.cap = "Graphs of primary productivity $(MgC~ha^-1~yr^-1)$ regressed against latitude. Lines of best fit are plotted according to the best model selected during analysis. All regressions are significant $(p<0.05)$. Plots show smaller component fluxes (1) and (2); the larger flux (3) defined by the combination of (1) and (2); and a modelled estimate of the sum of (1) and (2). 95% confidence intervals are plotted for (3)", fig.pos='H'}
  knitr::include_graphics("combined_stacked.png")
  ```

@@

  ```{r echo=FALSE, out.width='100%', fig.cap = "Plots of primary productivity $(MgC~ha^-1~yr^-1)$ regressed against the climate variables identified as the best predictors. Lines of best fit are plotted according to the best model selected during analysis. All regressions are significant $(p<0.05)$.", fig.pos='H'}
  knitr::include_graphics("combined_plots.png")
  ```

**Mean annual temperature.** All carbon fluxes show a linear increase with temperature.  
**Temperature seasonality.** Productivity is highest where temperature seasonality = 0. GPP, NPP, ANPP, and BNPP~root~ show a polynomial relationship with temperature seasonality. As seasonality increases, these variables show a more rapid decrease in productivity. ANPP~foliage~ and ANPP~woodystem~ show a linear relationship with temperature seasonality.  
**Annual temperature range.** As with temperature seasonality, productivity is highest at annual temperature ranges of 15$^\circ$C or lower. Again, GPP, NPP, ANPP, and BNPP~root~ show a polynomial relationship with temperature seasonality, and ANPP~foliage~ and ANPP~woodystem~ show a linear relationship with temperature seasonality.  
**Vapour pressure.** Productivity increases linearly with vapour pressure for all carbon fluxes, with the exception of ANPP~foliage~, which saturates at around 0.24.
